---
title: "House prices"
---

```{r setup}
library(keras)
housing <- dataset_boston_housing()
```

* variables
    + CRIM
        - per capita crime rate by town
    + ZN
        - proportion of residential land zoned for lots over 25,000 sq.ft.
    + INDUS
        - proportion of non-retail business acres per town.
    + CHAS
        - Charles River dummy variable (1 if tract bounds river; 0 otherwise)
    + NOX
        - nitric oxides concentration (parts per 10 million)
    + RM
        - average number of rooms per dwelling
    + AGE
        - proportion of owner-occupied units built prior to 1940
    + DIS
        - weighted distances to five Boston employment centres
    + RAD
        - index of accessibility to radial highways
    + TAX
        - full-value property-tax rate per $10,000
    + PTRATIO
        - pupil-teacher ratio by town
    + B
        - 1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town
    + LSTAT
        - % lower status of the population
    + MEDV
        - Median value of owner-occupied homes in $1000's

```{r variables}
naks <- as.data.frame(housing$train$x)
naks$y <-  housing$train$y
niks <- c(
  'CRIM',
  'ZN',
  'INDUS',
  'CHAS',
  'NOX',
  'RM',
  'AGE',
  'DIS',
  'RAD',
  'TAX',
  'PTRATIO',
  'B',
  'LSTAT',
  'MEDV'
  )
colnames(naks) <- niks
summary(naks)
```

```{r correlations}
library(corrplot)
corrplot(cor(as.matrix(naks)), method="circle")
```

```{r first_model}
fit <- lm(MEDV ~ ., data = naks)
summary(fit)
```

```{r first_model_visualization}
layout(matrix(c(1,2,3,4),2,2))
plot(fit)
```

```{r test_data}
plop <- as.data.frame(housing$test$x)
plop$y <-  housing$test$y
colnames(plop) <- niks
```

```{r first_model_analysis}
pred <- predict(fit, plop)
summary(pred)
actuals_preds <- data.frame(cbind(actuals=plop$MEDV, predicteds=pred))
cor(actuals_preds)
```

```{r variable_selection}
library(MASS)
step <- stepAIC(fit, direction="both")
step$anova # display results
```

```{r second_model}
fit_1 <- lm(MEDV ~ . - INDUS - AGE, data = naks)
summary(fit_1)
```

```{r second_model_visualization}
layout(matrix(c(1,2,3,4),2,2))
plot(fit_1)
```

```{r second_model_analysis}
pred_1 <- predict(fit_1, plop)
summary(pred_1)
actuals_preds_1 <- data.frame(cbind(actuals=plop$MEDV, predicteds=pred_1))
cor(actuals_preds_1)
```

```{r model_comparison}
anova(fit,fit_1)
```